The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

  To quantify the synchrotron radiation as a function of position,\
  we adopt\
  the default exponential model in \textsc{galprop} \citep{Strong2007}
  which has the following spatial dependence:\

>>>>

  To quantify the synchrotron radiation as a function of position,\
  we adopt the default exponential magnetic field in \textsc{galprop} \citep{Strong2007}
  which obeys the following spatial dependence:\
